---
title: ""
output:
  bookdown::pdf_document2:
    fig_crop: no
    fig_caption: yes
    toc: no
    number_sections: TRUE
    latex_engine: xelatex
  word_document: default
keep_tex: yes
header-includes:
- \usepackage[UKenglish]{isodate}
- \cleanlookdateon
- \usepackage{natbib}
- \bibliographystyle{agsm}
- \usepackage{hyperref}
- \usepackage{float}
- \usepackage[hang,flushmargin, bottom]{footmisc}
- \usepackage{sectsty}
- \usepackage{setspace}
- \usepackage{geometry}
<<<<<<< HEAD
- \usepackage{graphicx}
=======
>>>>>>> a147c139dae97e422257e52045e88315030ba2e6

bibliography: references.bib
---

\newgeometry{top=1.8in,bottom=1.8in,right=1in,left=1in}
\spacing{1.7}

\allsectionsfont{\centering}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{gobble}

\begin{centering}
  \newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
	\includegraphics[width=0.4\textwidth]{kuleuven_logo.png}\\[1cm]
	\textsc{\Large Collecting and Analyzing Big Data \\ for Social Sciences}\\[0.5cm]
	\textsc{\large B-KUL-S0K17A}\\[0.5cm]
	\HRule\\[0.6cm]
	{\huge\bfseries Assignment 2:} \\ [0.25cm]
	{\LARGE\bfseries Research Notebook}\\[0.2cm]
	\HRule\\[1.5cm]
	{\Large\textit{Group 24:}}\\
	\large Ekaterina \textsc{Zaitseva} - r0870363\\
	\large Emma \textsc{Schweidler} - r0883088 \\
	\large Jade \textsc{Willaert} - \\
	\vfill\vfill\vfill
	{\large\today}
	
\end{centering}

\allsectionsfont{\raggedright}

\singlespacing

 
\newpage

\newgeometry{top=1in,bottom=1in,right=1in,left=1in}
\pagenumbering{arabic} 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(formatR)
opts_chunk$set(tidy.opts=list(width.cutoff=90),tidy=TRUE)
```

<!-- Make sure following aspects are included: short problem statement & research question (without extensive literature review), methodological design, description of data (collection), data cleaning/wrangling steps, analysis, robustness checks (if applicable), results, limitations, conclusion, pitch -->

# Research Question

In March of this year, the Youtube channel \citet{JaidenAnimationsVideo} uploaded a video titled ‘Being Not Straight’. The animated story, which has since received almost 12 million views, is a coming out video that introduces the audience to aromanticism and asexuality. As both of these orientations are still relatively unknown, our project seeks to analyse the comment section under the video so as to investigate how the video was received. More precisely, we are interested in the audience's sentiment and the main topics discussed in the comments.

# Methodological Design

# Data

## Data Collection

`vosonSML` package vs `tuber` package

reported issues with `tuber` package: \citep{IssuesTuber}

issues with nested comments in general: \citep{IssuesNestedComments} 

```{r packages, message=F}
library(tidyverse)
library(tuber)
```

comments under the video at the time of data collection: 231,866

number of comments scraped with `tuber`: 180,743

number of comments scraped with `vosonSML`: 151,884

number of comments scraped with php tool \citep{RiederTools} (outwith R; only for benchmarking purposes): 218,848

noteworthy that none of the tested packages and tools were able to extract all Youtube comments

project in R, so we opted for the `tuber` package


code used to scrape comments (data were collected on 16th May 2022):

```{r tuber, eval=F }
# authenticate Youtube API (for security reasons, our personal APP_ID and APP_SECRET are not included in this script)
yt_oauth("APP_ID", "APP_SECRET", token = '')

# scrape comments
comments <- get_all_comments(video_id = "qF1DTK4U1AM")

# write output to file
write_csv(comments, "being_not_straight_16_may_22_tuber.csv")  
```


data import:

```{r data import}
# import data
comments <- read.csv("being_not_straight_16_may_22_tuber.csv", header = T)
```


## Data Wrangling

what metadata is available? what metadata is needed? drop columns if irrelevant

ignore replies and only focus on parent comment?

## Data Analysis

## Robustness Checks

# Results and Discussion

# Limitations

not all comments were scraped

# Conclusion

# Elevator Pitch

<<<<<<< HEAD
\newpage
\bibliography{references}
=======

\newpage
\bibliography{references}

>>>>>>> a147c139dae97e422257e52045e88315030ba2e6
